---
title: "Import and tidy data"
author: "Gerhard Riener and David Reinstein"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

# Install packages

<<<<<<< HEAD
=======
```{r package install, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
install.packages(c(
    "tidyverse",
    "viridis",
    "broom"
))

```

>>>>>>> c4aba5ad574f341c1c2b79e8493af2567f728d57
```{r message=FALSE, warning=FALSE}
# library(tidyverse)
library("dplyr")
library("broom")
library("tidyr")
library("readr")
```

# Data organisation

```{r}
# gerhard_dir <- "~/gerhard.riener@gmail.com/"
# data_archive <- "~/gerhard.riener@gmail.com/substitution_experiment_is_back/Data/"
# data_build <- "~/gerhard.riener@gmail.com/substitution_experiment_is_back/Build/Data/"
# list_of_files <- list.files(data_archive, ".csv$",recursive = T) 
# ".py$" is the type of file you want to copy. Remove if copying all types of files. 
# file.copy(file.path(data_archive,list_of_files), data_build)
```


# Import data (Omnibus-linked study only, for now)

*DR: are these importing as tibbles?* GR: yes, everything is tibble here

```{r message=FALSE, warning=FALSE}
<<<<<<< HEAD
StudentsFirstAsk <- read_csv("data/StudentsFirstAsk.csv")
StudentsSecondAsk <- read_delim("data/StudentsSecondAsk.csv", "\t", escape_double = FALSE, trim_ws = TRUE) #somehow this one was tab delimited 

col_names <- names(read_csv("data/NonstudentsFirstAsk.csv", n_max = 0))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow?

NonstudentsFirstAsk <- read_csv("data/NonstudentsFirstAsk.csv", col_names = col_names, skip = 3)
NonstudentsSecondAsk <- read_csv("data/NonstudentsSecondAsk.csv")
=======
StudentsFirstAsk <- read_csv("../data/StudentsFirstAsk.csv")
StudentsSecondAsk <- read_delim("../data/StudentsSecondAsk.csv", "\t", escape_double = FALSE, trim_ws = TRUE) #somehow this one was tab delimited 

col_names <- names(read_csv("../data/NonstudentsFirstAsk.csv", n_max = 0))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow?

NonstudentsFirstAsk <- read_csv("../data/NonstudentsFirstAsk.csv", col_names = col_names, skip = 3)
NonstudentsSecondAsk <- read_csv("../data/NonstudentsSecondAsk.csv")
>>>>>>> c4aba5ad574f341c1c2b79e8493af2567f728d57
```

*DR:* I suggest we might deal with the 'omnibus survey responses' as separate files and separate code blocks. These are coded slightly differently for students and nonstudents. Also, these come with the 'second ask' for nonstudents but with the 'first ask' for students.

## First ask

Stack students and non-students

```{r warning=FALSE}
#Start and end dates (times?) in R format for Omnibus:  
StudentsFirstAsk$StartDate<-as.POSIXct(StudentsFirstAsk$StartDate, tz = "GMT")
StudentsFirstAsk$EndDate<-as.POSIXct(StudentsFirstAsk$EndDate, tz = "GMT")
StudentsFirstAsk$RecordedDate<-as.POSIXct(StudentsFirstAsk$RecordedDate, tz = "GMT") #DR: I think this only differs if we 'closed' an unfinished survey
StudentsFirstAsk$Finished<-as.logical(StudentsFirstAsk$Finished)

StudentsFirstAsk$Student <- rep(1,nrow(StudentsFirstAsk)) #A vector of 1's to define this as a 'student'

NonstudentsFirstAsk$Finished<-as.logical(NonstudentsFirstAsk$Finished)
NonstudentsFirstAsk$Student <- rep(0,nrow(NonstudentsFirstAsk))

FirstAsk <- bind_rows(StudentsFirstAsk,NonstudentsFirstAsk) #stacks the rows for students and nonstudents; hope they have the same variable names

FirstAsk <- filter(FirstAsk, firstasktreat == "noask" | firstasktreat == "international_ha" | firstasktreat == "international_hb" | firstasktreat == "domestic_happyafter" | firstasktreat == "domestic_happyfirst" | firstasktreat == "domestic_ha" | firstasktreat == "domestic_hb"  | firstasktreat == "international_happybefore" | firstasktreat == "international_happyafter") #Removes before/after treatments here. (DR: might later recover for fancy statistics?)

```

## Second ask
```{r}
NonstudentsSecondAsk$Finished<-as.logical(NonstudentsSecondAsk$Finished)
StudentsSecondAsk$Finished<-as.logical(StudentsSecondAsk$Finished)

StudentsSecondAsk$StartDate <- as.POSIXct(StudentsSecondAsk$StartDate,"%d.%m.%Y %H:%M", tz = "GMT")
StudentsSecondAsk$EndDate <- as.POSIXct(StudentsSecondAsk$EndDate, "%d.%m.%Y %H:%M",tz = "GMT")

NonstudentsSecondAsk$StartDate <- as.POSIXct(NonstudentsSecondAsk$StartDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$EndDate <- as.POSIXct(NonstudentsSecondAsk$EndDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$RecordedDate <- as.POSIXct(NonstudentsSecondAsk$RecordedDate, "%d/%m/%Y %H:%M",tz = "GMT")

SecondAsk <- bind_rows(StudentsSecondAsk,NonstudentsSecondAsk)

```

## Stack first and second ask
```{r message=FALSE, warning=FALSE, include=FALSE}

AskData <- bind_rows(FirstAsk, SecondAsk)

AskData <- AskData[colSums(!is.na(AskData)) > 0] #removes rows with only missing data

AskData$happiness_1_2 <- as.factor(AskData$happiness_1_2 )
AskData$happiness_1   <- as.factor(AskData$happiness_1)
AskData$happiness_1_3 <- as.factor(AskData$happiness_1_3)
AskData$happiness_1_1 <- as.factor(AskData$happiness_1_1)


DonationVars <- c("s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb", "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha")

AskData$AllDonations <- rowSums(AskData[,DonationVars], na.rm=TRUE)

#DR: maybe keep fewer variables here, or at least put aside the omnibus survey variables and deal with these later

keepVars <- c("ResponseId","code","RecruitmentID","AllDonations","s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb",  "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha", "happiness_1_1", "happiness_1_2",  "happiness_1_3", "happiness_1", "current_happiness_1",   "s1happyafter_int_1",  "s1happynoask_1", "s1happynoask_1_1", "Q174", "Q175", "SEX", "BIRTH", "RACE", "RELIG",  "SINGLE", "UNI STDNT", "STUDIES", "PREV PAR", "EXP PREF", "MOMJOB",  "DADJOB", "MOMEDUC", "DADEDUC", "SIBLINGS", "SIBORDER", "CHILD",  "NUMCHILD", "birth_nation", "ABROAD", "NATION", "ENGYEARS", "FIRSTLANG",  "FLUENT", "HOMELANG", "LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2",  "OTR_COUNTRY1_3", "OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3",  "ATTRIBUTES_1", "ATTRIBUTES_2", "ATTRIBUTES_3", "ATTRIBUTES_4",  "ATTRIBUTES_5", "ATTRIBUTES_6", "ATTRIBUTES_7", "ATTRIBUTES_8",  "ATTRIBUTES_9", "ATTRIBUTES_10", "POWER", "ACHIEVE", "HEDON",  "STIMUL", "SELFD", "UNIVE", "BENEV", "TRADI", "CONFO", "SECUR",  "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS",  "RESPECT", "USELESS", "NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL",  "ANIMO", "PACT", "CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1",  "auth2", "auth3", "auth4", "EYES1", "EYES2", "EYES3", "EYES4",  "EYES5", "EYES6", "EYES7", "EYES8", "EYES9", "EYES10", "EYES11",  "EYES12", "EYES13", "EYES14", "EYES15", "EYES16", "EYES17", "EYES18",  "RISK", "trust", "decisionmode", "likert_time_recip_1", "likert_time_recip_2",  "likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1",  "social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5",  "ineq", "ownership", "merit", "IMPAIR", "MENT",   "Q51", "gender",  "firstasktreat",   "S1Reward", "Student",   "sex", "childpresentmdl",  "clustergroup", "ordergroup", "recruitmentid", "title", "rand_num",  "rankingroup", "groupn", "reminderperson",  "Gift", "BHFExtra", "OxfamExtra", "TotalExtra",  "ResponseID", "ResponseSet", "thankyouemploy", "Q40", "vignettebackground",  "interviewers", "answersmatter", "salaryrequest1", "medsalaryguess",  "medsalarytold", "Q35", "vignetteagain", "Q36", "salaryrequest2",  "Q23", "anspctgradjob", "guesspctwork", "anspctwork", "guessavgsalary",  "ansavgsalary", "Q17_1_TEXT", "Q17_2_TEXT", "Q17_3_TEXT", "Q17_4_TEXT",  "Q18_1_TEXT", "Q18_2_TEXT", "Q18_3_TEXT", "Q18_4_TEXT",  "ask_stc_10_mx25", "ask_cruk_10_mx25a", "Q19", "DO-BR-FL_21",  "DO-BR-FL_22", "DO-BR-FL_100", "DO-BR-FL_132", "DO-BR-FL_133",  "DO-BR-FL_138", "DO-BR-FL_120", "DO-BR-FL_121", "DO-BR-FL_126",  "DO-BR-FL_108", "DO-BR-FL_109", "DO-BR-FL_114", "DO-BR-FL_144",  "DO-BR-FL_145", "DO-BR-FL_150", "DO-BR-FL_158", "DO-BR-FL_159",  "DO-BR-FL_164", "Q144", "Q145", "Q46", "Q47", "Q48", "Q49", "Q50",  "Q53", "Q54", "Q56", "Q57", "Q58", "Q59", "Q60", "Q61", "Q62",  "Q63", "Q64", "Q65", "Q66", "Q67", "Q68", "Q69", "Q70", "Q71",  "Q72_1", "Q72_2", "Q72_3", "Q73_1", "Q73_2", "Q73_3", "Q75_1",  "Q75_2", "Q75_3", "Q75_4", "Q75_5", "Q75_6", "Q75_7", "Q75_8",  "Q75_9", "Q75_10", "Q77", "Q78", "Q79", "Q80", "Q81", "Q83",  "Q84", "Q85", "Q86", "Q87", "Q89", "Q90", "Q91", "Q92", "Q93",  "Q95", "Q96", "Q97", "Q98", "Q99", "Q101", "Q102", "Q103", "Q104",  "Q105", "Q107", "Q108", "Q109", "Q110", "Q111", "Q151", "Q152",  "Q153", "Q154", "Q113", "Q114", "Q115", "Q116", "Q117", "Q118",  "Q120", "Q121", "Q122", "Q123", "Q124", "Q125", "Q127", "Q128",  "Q129", "Q130", "Q131", "Q132", "Q146", "Q147", "Q148", "Q149_1",  "Q149_2", "Q149_3", "Q134", "Q135", "Q136_1", "Q136_2", "Q136_3",  "Q136_4", "Q136_5", "Q138", "Q139", "Q140", "Q141", "Q142",  "StartDate", "EndDate")

# Variables names for renaming
VarNames1 <- c("ResponseId", "code", "RecruitmentID","AllDonations","s1_don_int_ha","OxfamDonation", "BHFDonation", "TotalDonation","ns1_donint_ha","ns2_don_dom_hb", "ns2_don_dom_ha", "S1Donation", "ns1_dondom_ha","s1_don_int_hb", "ns2_don_int_hb", "ns2_don_int_ha", "happiness_1_1","happiness_1_2", "happiness_1_3", "happiness_1", "current_happiness_1","s1happyafter_int_1", "s1happynoask_1", "s1happynoask_1_1", "Q174","Q175", "SEX", "BIRTH", "RACE", "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2", "OTR_COUNTRY1_3","OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3", "ATTRIBUTES_1","ATTRIBUTES_2", "ATTRIBUTES_3", "ATTRIBUTES_4", "ATTRIBUTES_5","ATTRIBUTES_6", "ATTRIBUTES_7", "ATTRIBUTES_8", "ATTRIBUTES_9","ATTRIBUTES_10", "POWER", "ACHIEVE", "HEDON", "STIMUL", "SELFD","UNIVE", "BENEV", "TRADI", "CONFO", "SECUR", "WORTH", "GOODQ","FAIL", "COMPAR", "PROUD", "POSAT", "SATIS", "RESPECT", "USELESS","NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL", "ANIMO", "PACT","CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1", "auth2", "auth3","auth4", "EYES1", "EYES2", "EYES3", "EYES4", "EYES5", "EYES6","EYES7", "EYES8", "EYES9", "EYES10", "EYES11", "EYES12", "EYES13","EYES14", "EYES15", "EYES16", "EYES17", "EYES18", "RISK", "trust","decisionmode", "likert_time_recip_1", "likert_time_recip_2","likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1","social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5","ineq", "ownership", "merit", "IMPAIR", "MENT", "Q51", "gender","firstasktreat", "S1Reward", "Student", "sex", "childpresentmdl","clustergroup", "ordergroup", "recruitmentid", "title", "rand_num","rankingroup", "groupn", "reminderperson", "Gift", "BHFExtra","OxfamExtra", "TotalExtra", "ResponseID", "ResponseSet", "thankyouemploy","Q40", "vignettebackground", "interviewers", "answersmatter","salaryrequest1", "medsalaryguess", "medsalarytold", "Q35", "vignetteagain","Q36", "salaryrequest2", "Q23", "anspctgradjob", "guesspctwork","anspctwork", "guessavgsalary", "ansavgsalary", "Q17_1_TEXT","Q17_2_TEXT", "Q17_3_TEXT", "Q17_4_TEXT", "Q18_1_TEXT", "Q18_2_TEXT","Q18_3_TEXT", "Q18_4_TEXT", "ask_stc_10_mx25", "ask_cruk_10_mx25a","Q19", "DO-BR-FL_21", "DO-BR-FL_22", "DO-BR-FL_100", "DO-BR-FL_132","DO-BR-FL_133", "DO-BR-FL_138", "DO-BR-FL_120", "DO-BR-FL_121","DO-BR-FL_126", "DO-BR-FL_108", "DO-BR-FL_109", "DO-BR-FL_114","DO-BR-FL_144", "DO-BR-FL_145", "DO-BR-FL_150", "DO-BR-FL_158","DO-BR-FL_159", "DO-BR-FL_164", "Q144", "Q145", "Gender2", "BirthData","Ethnicity", "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3", "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "ImportantPower", "ImportantSuccess", "ImportantHedonsim", "ImportantStimulation","ImportantCreativity", "ImportantUniversalism", "ImpportantBenevolence", "ImportantTradition", "ImportantConformity", "ImportantSecurity", "SelfEsteemWorth", "SelfEsteemQuality", "SelfEsteemFailure","SelfEsteemGoodWork", "SelfEsteemNoProud", "SelfEsteemPositive", "SelfEsteemSatisfied", "SelfEsteemLittleRespect", "SelfEsteemUseless", "SelfEsteemNoGood", "LinguistTestSpace", "LinguistTestBroaden","LinguistTestEmanate", "LinguistTestEdible", "LinguistTestAnimosity", "LinguistTestPact", "LinguistTestCloistered", "LinguistTestCaprice","LinguistTestAccustom")

VarNames2 <- c("LinguistTestAllusion" ,"ImportantIndependence","ImportantCuriosity", "ImportantSelfReliance", "ImportantConsiderate", "Q113", "Q114", "Q115", "Q116","Q117", "Q118", "Q120", "Q121", "Q122", "Q123", "Q124", "Q125","Q127", "Q128", "Q129", "Q130", "Q131", "Q132", "RiskAversion", "GeneralTrust","DecisionIntuitive", "Q149_1", "Q149_2", "Q149_3", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivcorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight", "ImpairmentDescription", "StartDate", "EndDate")

VarNames <- c(VarNames1,VarNames2)

AskData <- select(AskData, keepVars)

colnames(AskData) <- VarNames


# Write out all Variable names into c() format
# dput(names(AskData), file="Variables.txt")

```

## Merge data columns

We have a lot of variables that record the same but are labeled differently in different experiments. Try to merge those. DR: Maybe Anka can help with this


```{r}


varsReplace <- c("SEX", "BIRTH", "RACE")#, "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2", "OTR_COUNTRY1_3","OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3")

varsKeepReplace <- c("Gender2", "BirthData","Ethnicity")#, "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3")



IterateReplace <- function(rd,kd) {
  AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd))
}


IterateReplace("Gender2","SEX")

AskData$BirthData <- with(AskData,ifelse(is.na(BirthData),BIRTH,BirthData))

mapply(function(rd,kd) AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd), rd = varsKeep, rd = varsKeepReplace))

# Save merged data
write_csv(AskData, "../output/AskData.csv") 


```
