---
title: "Import and tidy data"
author: "Gerhard Riener and David Reinstein"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---


# Load Packages
```{r message=FALSE, warning=FALSE}
library("tidyverse")
library("broom")
library("dataMaid")
library("qualtRics")
```

  
# Import data (Omnibus-linked study only, for now)


Trying alternate input:
DR, @GR -- the "readSurvey" function doesn't do much I guess 

```{r message=FALSE, warning=FALSE}
#Input nonstudents first ask 
col_names_NS1 <- names(read_csv("../data/NonstudentsFirstAsk_full.csv", n_max = 0))  
col_description_NS1 <- names(read_csv("../data/NonstudentsFirstAsk_full.csv", n_max = 0,skip=1)) #Row 2 gives the question text
NonstudentsFirstAsk <- read_csv("../data/NonstudentsFirstAsk_full.csv", col_names = col_names_S1, skip = 3)

#Input nonstudents second ask (Includes Omnibus, but coding/content differs from students version slightly)
col_names_NS2 <- names(read_csv("../data/NonstudentsSecondAsk_full.csv", n_max = 0))  
col_description_NS2 <- names(read_csv("../data/NonstudentsSecondAsk_full.csv", n_max = 0,skip=1)) #Row 2 gives the question text
NonstudentsSecondAsk <- read_csv("../data/NonstudentsSecondAsk_full.csv", col_names = col_names_S1, skip = 3)

#Input students first ask (includes Omnibus, student coding differs slightly from nonstudent version)
col_names_S1 <- names(read_csv("../data/StudentsFirstAsk_full.csv", n_max = 0))  
col_description_S1 <- names(read_csv("../data/StudentsFirstAsk_full.csv", n_max = 0,skip=1)) #Row 2 gives the question text
StudentsFirstAsk <- read_csv("../data/StudentsFirstAsk_full.csv", col_names = col_names_S1, skip = 3)


#Input students second ask (paired with employability questions)
col_names_S2 <- names(read_csv("../data/StudentsSecondAsk_full.csv", n_max = 0))  
col_description_S2 <- names(read_csv("../data/StudentsSecondAsk_full.csv", n_max = 0,skip=1)) #Row 2 gives the question text
StudentsSecondAsk <- read_csv("../data/StudentsSecondAsk_full.csv", col_names = col_names_S1, skip = 3)
```

Note: These are imported from .csv  files downloaded from Qualtrics.

#DR, @GR: I suggest cutting the following chunk, and adapting the previous chunk instead...
```{r message=FALSE, warning=FALSE}

col_names <- names(read_csv("../data/NonstudentsFirstAsk.csv", n_max = 0))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow?

NonstudentsFirstAsk <- read_csv("../data/NonstudentsFirstAsk.csv", col_names = col_names, skip = 3)
NonstudentsSecondAsk <- read_csv("../data/NonstudentsSecondAsk.csv")
StudentsFirstAsk <- read_csv("../data/StudentsFirstAsk.csv")
StudentsSecondAsk <- read_delim("../data/StudentsSecondAsk.csv", "\t", escape_double = FALSE, trim_ws = TRUE) #somehow this one was tab delimited 

```

*DR:* I suggest we might deal with the 'omnibus survey responses' as separate files and separate code blocks. These are coded slightly differently for students and nonstudents. Also, these come with the 'second ask' for nonstudents but with the 'first ask' for students.

## First ask

Stack students and non-students

```{r warning=FALSE}
#Start and end dates (times?) in R format for Omnibus:  
StudentsFirstAsk$StartDate<-as.POSIXct(StudentsFirstAsk$StartDate, tz = "GMT")
StudentsFirstAsk$EndDate<-as.POSIXct(StudentsFirstAsk$EndDate, tz = "GMT")
StudentsFirstAsk$RecordedDate<-as.POSIXct(StudentsFirstAsk$RecordedDate, tz = "GMT") #DR: I think this only differs if we 'closed' an unfinished survey
StudentsFirstAsk$Finished<-as.logical(StudentsFirstAsk$Finished)

StudentsFirstAsk$Student <- rep(1,nrow(StudentsFirstAsk)) #A vector of 1's to define this as a 'student'

NonstudentsFirstAsk$Finished<-as.logical(NonstudentsFirstAsk$Finished)
NonstudentsFirstAsk$Student <- rep(0,nrow(NonstudentsFirstAsk))
NonstudentsFirstAsk$code <- as.character(NonstudentsFirstAsk$RecruitmentID)
NonstudentsFirstAsk$code <- ifelse(is.na(NonstudentsFirstAsk$code), as.character(NonstudentsFirstAsk$recruitmentid), NonstudentsFirstAsk$code )


FirstAsk <- bind_rows(StudentsFirstAsk,NonstudentsFirstAsk) #stacks the rows for students and nonstudents; hope they have the same variable names

FirstAsk <- filter(FirstAsk, firstasktreat == "noask" | firstasktreat == "international_ha" | firstasktreat == "international_hb" | firstasktreat == "domestic_happyafter" | firstasktreat == "domestic_happyfirst" | firstasktreat == "domestic_ha" | firstasktreat == "domestic_hb"  | firstasktreat == "international_happybefore" | firstasktreat == "international_happyafter") #Removes before/after treatments here. (DR: might later recover for fancy statistics?)
FirstAsk$Stage <- 1
```

## Second ask
```{r}
NonstudentsSecondAsk$Finished<-as.logical(NonstudentsSecondAsk$Finished)
StudentsSecondAsk$Finished<-as.logical(StudentsSecondAsk$Finished)

StudentsSecondAsk$StartDate <- as.POSIXct(StudentsSecondAsk$StartDate,"%d.%m.%Y %H:%M", tz = "GMT")
StudentsSecondAsk$EndDate <- as.POSIXct(StudentsSecondAsk$EndDate, "%d.%m.%Y %H:%M",tz = "GMT")

NonstudentsSecondAsk$StartDate <- as.POSIXct(NonstudentsSecondAsk$StartDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$EndDate <- as.POSIXct(NonstudentsSecondAsk$EndDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$RecordedDate <- as.POSIXct(NonstudentsSecondAsk$RecordedDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$code <- as.character(NonstudentsSecondAsk$RecruitmentID)
NonstudentsSecondAsk$code <- ifelse(is.na(NonstudentsSecondAsk$code), as.character(NonstudentsSecondAsk$recruitmentid), NonstudentsSecondAsk$code )


SecondAsk <- bind_rows(StudentsSecondAsk,NonstudentsSecondAsk)
SecondAsk$Stage <- 2

```

## Stack first and second ask
```{r message=FALSE, warning=FALSE, include=FALSE}

AskData <- bind_rows(FirstAsk, SecondAsk)

AskData <- AskData[colSums(!is.na(AskData)) > 0] #removes rows with only missing data

AskData$happiness_1_2 <- as.factor(AskData$happiness_1_2)
AskData$happiness_1   <- as.factor(AskData$happiness_1)
AskData$happiness_1_3 <- as.factor(AskData$happiness_1_3)
AskData$happiness_1_1 <- as.factor(AskData$happiness_1_1)


DonationVars <- c("s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb", "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb")

DonationVarsFix <- c("ask_stc_10_mx25", "ask_cruk_10_mx25a", "ns2_don_int_hb", "ns2_don_int_ha", "ns2_don_dom_hb", "ns2_don_dom_ha")
#does firstasktreat belong in the above list? 

# This sum seems to doublecount things
AskData$AllDonations <- rowSums(AskData[,DonationVars], na.rm=TRUE)

#AskData$AllDonationsFix <- rowSums(AskData[,DonationVarsFix], na.rm=TRUE)

#DR: maybe keep fewer variables here, or at least put aside the omnibus survey variables and deal with these later

keepVars <- c("ResponseId","code","RecruitmentID","AllDonations","s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb",  "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb", "happiness_1_1", "happiness_1_2",  "happiness_1_3", "happiness_1", "current_happiness_1",   "s1happyafter_int_1",  "s1happynoask_1", "s1happynoask_1_1", "Q174", "Q175", "SEX", "BIRTH", "RACE", "RELIG",  "SINGLE", "UNI STDNT", "STUDIES", "PREV PAR", "EXP PREF", "MOMJOB",  "DADJOB", "MOMEDUC", "DADEDUC", "SIBLINGS", "SIBORDER", "CHILD",  "NUMCHILD", "birth_nation", "ABROAD", "NATION", "ENGYEARS", "FIRSTLANG",  "FLUENT", "HOMELANG", "LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2",  "OTR_COUNTRY1_3", "OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3",  "ATTRIBUTES_1", "ATTRIBUTES_2", "ATTRIBUTES_3", "ATTRIBUTES_4",  "ATTRIBUTES_5", "ATTRIBUTES_6", "ATTRIBUTES_7", "ATTRIBUTES_8",  "ATTRIBUTES_9", "ATTRIBUTES_10", "POWER", "ACHIEVE", "HEDON",  "STIMUL", "SELFD", "UNIVE", "BENEV", "TRADI", "CONFO", "SECUR",  "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS",  "RESPECT", "USELESS", "NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL",  "ANIMO", "PACT", "CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1",  "auth2", "auth3", "auth4", "EYES1", "EYES2", "EYES3", "EYES4",  "EYES5", "EYES6", "EYES7", "EYES8", "EYES9", "EYES10", "EYES11",  "EYES12", "EYES13", "EYES14", "EYES15", "EYES16", "EYES17", "EYES18",  "RISK", "trust", "decisionmode", "likert_time_recip_1", "likert_time_recip_2",  "likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1",  "social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5",  "ineq", "ownership", "merit", "IMPAIR", "MENT",   "Q51", "gender",  "firstasktreat",   "S1Reward", "Student",   "sex", "childpresentmdl",  "clustergroup", "ordergroup", "recruitmentid", "title", "rand_num",  "rankingroup", "groupn", "reminderperson",  "Gift", "BHFExtra", "OxfamExtra", "TotalExtra",  "ResponseID", "ResponseSet", "thankyouemploy", "Q40", "vignettebackground",  "interviewers", "answersmatter", "salaryrequest1", "medsalaryguess",  "medsalarytold", "Q35", "vignetteagain", "Q36", "salaryrequest2",  "Q23", "anspctgradjob", "guesspctwork", "anspctwork", "guessavgsalary",  "ansavgsalary", "Q17_1_TEXT", "Q17_2_TEXT", "Q17_3_TEXT", "Q17_4_TEXT",  "Q18_1_TEXT", "Q18_2_TEXT", "Q18_3_TEXT", "Q18_4_TEXT",  "ask_stc_10_mx25", "ask_cruk_10_mx25a", "Q19", "DO-BR-FL_21",  "DO-BR-FL_22", "DO-BR-FL_100", "DO-BR-FL_132", "DO-BR-FL_133",  "DO-BR-FL_138", "DO-BR-FL_120", "DO-BR-FL_121", "DO-BR-FL_126",  "DO-BR-FL_108", "DO-BR-FL_109", "DO-BR-FL_114", "DO-BR-FL_144",  "DO-BR-FL_145", "DO-BR-FL_150", "DO-BR-FL_158", "DO-BR-FL_159",  "DO-BR-FL_164", "Q144", "Q145", "Q46", "Q47", "Q48", "Q49", "Q50",  "Q53", "Q54", "Q56", "Q57", "Q58", "Q59", "Q60", "Q61", "Q62",  "Q63", "Q64", "Q65", "Q66", "Q67", "Q68", "Q69", "Q70", "Q71",  "Q72_1", "Q72_2", "Q72_3", "Q73_1", "Q73_2", "Q73_3", "Q75_1",  "Q75_2", "Q75_3", "Q75_4", "Q75_5", "Q75_6", "Q75_7", "Q75_8",  "Q75_9", "Q75_10", "Q77", "Q78", "Q79", "Q80", "Q81", "Q83",  "Q84", "Q85", "Q86", "Q87", "Q89", "Q90", "Q91", "Q92", "Q93",  "Q95", "Q96", "Q97", "Q98", "Q99", "Q101", "Q102", "Q103", "Q104",  "Q105", "Q107", "Q108", "Q109", "Q110", "Q111", "Q151", "Q152",  "Q153", "Q154", "Q113", "Q114", "Q115", "Q116", "Q117", "Q118",  "Q120", "Q121", "Q122", "Q123", "Q124", "Q125", "Q127", "Q128",  "Q129", "Q130", "Q131", "Q132", "Q146", "Q147", "Q148", "Q149_1",  "Q149_2", "Q149_3", "Q134", "Q135", "Q136_1", "Q136_2", "Q136_3",  "Q136_4", "Q136_5", "Q138", "Q139", "Q140", "Q141", "Q142",  "StartDate", "EndDate", "Stage")


VarNames2 <- c("LinguistTestCloistered", "LinguistTestCaprice", "LinguistTestAccustom", "LinguistTestAllusion", "ImportantIndependence", "ImportantCuriosity", "ImportantSelfReliance", "ImportantConsiderate", "Q113", "Q114", "Q115", "Q116","Q117", "Q118", "Q120", "Q121", "Q122", "Q123", "Q124", "Q125","Q127", "Q128", "Q129", "Q130", "Q131", "Q132", "RiskAversion", "GeneralTrust","DecisionIntuitive", "Q149_1", "Q149_2", "Q149_3", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivcorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight", "ImpairmentDescription", "StartDate", "EndDate", "Stage")

# Variables names for renaming

VarNames1 <- c("ResponseId", "code", "RecruitmentID","AllDonations","s1_don_int_ha", "OxfamDonation", "BHFDonation", "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb", "ns2_don_dom_ha", "S1Donation", "ns1_dondom_ha", "s1_don_int_hb", "ns2_don_int_hb", "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb", "happiness_1_1", "happiness_1_2", "happiness_1_3", "happiness_1", "current_happiness_1","s1happyafter_int_1", "s1happynoask_1", "s1happynoask_1_1", "Q174","Q175", "SEX", "BIRTH", "RACE", "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2", "OTR_COUNTRY1_3","OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3", "ATTRIBUTES_1","ATTRIBUTES_2", "ATTRIBUTES_3", "ATTRIBUTES_4", "ATTRIBUTES_5","ATTRIBUTES_6", "ATTRIBUTES_7", "ATTRIBUTES_8", "ATTRIBUTES_9","ATTRIBUTES_10", "POWER", "ACHIEVE", "HEDON", "STIMUL", "SELFD","UNIVE", "BENEV", "TRADI", "CONFO", "SECUR", "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS", "RESPECT", "USELESS","NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL", "ANIMO", "PACT","CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1", "auth2", "auth3","auth4", "EYES1", "EYES2", "EYES3", "EYES4", "EYES5", "EYES6","EYES7", "EYES8", "EYES9", "EYES10", "EYES11", "EYES12", "EYES13","EYES14", "EYES15", "EYES16", "EYES17", "EYES18", "RISK", "trust","decisionmode", "likert_time_recip_1", "likert_time_recip_2","likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1","social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5","ineq", "ownership", "merit", "IMPAIR", "MENT", "Q51", "gender","firstasktreat", "S1Reward", "Student", "sex", "childpresentmdl","clustergroup", "ordergroup", "recruitmentid", "title", "rand_num","rankingroup", "groupn", "reminderperson", "Gift", "BHFExtra","OxfamExtra", "TotalExtra", "ResponseID", "ResponseSet", "thankyouemploy","Q40", "vignettebackground", "interviewers", "answersmatter","salaryrequest1", "medsalaryguess", "medsalarytold", "Q35", "vignetteagain","Q36", "salaryrequest2", "Q23", "anspctgradjob", "guesspctwork","anspctwork", "guessavgsalary", "ansavgsalary", "Q17_1_TEXT","Q17_2_TEXT", "Q17_3_TEXT", "Q17_4_TEXT", "Q18_1_TEXT", "Q18_2_TEXT","Q18_3_TEXT", "Q18_4_TEXT", "ask_stc_10_mx25", "ask_cruk_10_mx25a","Q19", "DO-BR-FL_21", "DO-BR-FL_22", "DO-BR-FL_100", "DO-BR-FL_132","DO-BR-FL_133", "DO-BR-FL_138", "DO-BR-FL_120", "DO-BR-FL_121","DO-BR-FL_126", "DO-BR-FL_108", "DO-BR-FL_109", "DO-BR-FL_114","DO-BR-FL_144", "DO-BR-FL_145", "DO-BR-FL_150", "DO-BR-FL_158","DO-BR-FL_159", "DO-BR-FL_164", "Q144", "Q145", "Gender2", "BirthData","Ethnicity", "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3", "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "ImportantPower", "ImportantSuccess", "ImportantHedonsim", "ImportantStimulation","ImportantCreativity", "ImportantUniversalism", "ImpportantBenevolence", "ImportantTradition", "ImportantConformity", "ImportantSecurity", "SelfEsteemWorth", "SelfEsteemQuality", "SelfEsteemFailure", "SelfEsteemGoodWork", "SelfEsteemNoProud", "SelfEsteemPositive", "SelfEsteemSatisfied", "SelfEsteemLittleRespect", "SelfEsteemUseless", "SelfEsteemNoGood", "LinguistTestSpace", "LinguistTestBroaden","LinguistTestEmanate", "LinguistTestEdible", "LinguistTestAnimosity", "LinguistTestPact")

# Further fixes

AskData$firstasktreat <- ifelse(is.na(AskData$firstasktreat) & is.na(AskData$OxfamDonation), "international_happyfirst", AskData$firstasktreat)
    


VarNames <- c(VarNames1,VarNames2)

AskData <- select(AskData, keepVars)

colnames(AskData) <- VarNames

```

## Merge data columns

We have a lot of variables that record the same but are labeled differently in different experiments. Try to merge those. DR: Maybe Anka can help with this


```{r}
#DR: I assume this is making common variable names/labels for key variables across the surveys 

varsReplace <- c("SEX", "BIRTH", "RACE")#, "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2", "OTR_COUNTRY1_3","OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3")

varsKeepReplace <- c("Gender2", "BirthData","Ethnicity")#, "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3")


IterateReplace <- function(rd,kd) {
  AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd))
}

IterateReplace("Gender2","SEX")

AskData$BirthData <- with(AskData,ifelse(is.na(BirthData),BIRTH,BirthData))

mapply(function(rd,kd) AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd), rd = varsKeep, rd = varsKeepReplace))

# Save merged data
write_csv(AskData, "../output/AskData.csv") 

```
# TODO to make the data tidy

Our data is not tidy yet for the analysis. We need to make the dataset longer with the variable "Donation" as the main variable and Ask $\in {1,2}$ to indicate first and second ask and the charity they could donate to. 

We have the donation variables s1_don_int_ha, OxfamDonation, BHFDonation, ns1_donint_ha, ns2_don_dom_hb, ns2_don_dom_ha, S1Donation, ns1_don_dom_ha, s1_don_int_hb, ns2_don_int_hb, ns2_don_int_ha

**DR: The following should define the treatments**

- Nonstudents: firstasktreat (same variable in both csv files) for first ask, combined with whichever is nonmissing among (ns2_don_int_hb, ns2_don_int_ha, ns2_don_dom_hb, ns2_don_dom_ha) for the second ask (if one of the first two are present it is the international second ask, if one of the latter two are present it's the domestic second ask).
  - In the raw data I find 97 entries with a firstasktreat recorded as well as a nonmissing value for one of the aforementioned ns2 variables.

- Students:  firstasktreat (same variable in both csv files) for first ask, combined with whichever is nonmissing among ask_stc_10_mx25 and ask_cruk_10_mx25a for the second ask (the former is international, the latter is domestic).  
  - In the raw data I find 142 obs with a firstasktreat recorded as well as a nonmissing value for one of ask_stc... or ask_cruk... 

```{r}
#coding the main treatment "CharityTreat"
AskData <- AskData %>% mutate(CharityTreat = case_when(!is.na(ask_cruk_10_mx25a) & firstasktreat == "domestic_ha"  ~ "Domestic-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "domestic_happyfirst"       ~ "Domestic-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "domestic_hb"               ~ "Domestic-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "domestic_happyafter"       ~ "Domestic-Domestic",
                                                      o
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "domestic_ha"  ~ "Domestic-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "domestic_happyfirst"       ~ "Domestic-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "domestic_hb"               ~ "Domestic-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "domestic_happyafter"       ~ "Domestic-Internat.",
                                                       
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "international_happyafter"  ~ "Internat.-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "international_ha"          ~ "Internat.-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "international_hb"          ~ "Internat.-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "international_happyfirst"  ~ "Internat.-Domestic",
                                                       
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "international_happyafter"  ~ "Internat.-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "international_ha"          ~ "Internat.-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "international_hb"          ~ "Internat.-Internat.",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "international_happyfirst"  ~ "Internat.-Internat.",
                                                       
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "noask"  ~ "No ask-Domestic",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "noask"  ~ "No ask-Internat."
                                                      )) 

AskData$CharityTreat <- as.factor(AskData$CharityTreat)

AskData$Charity <- NA
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(BHFDonation), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(OxfamDonation), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_int_ha), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_int_hb), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_dom_ha), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_dom_hb), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ask_stc_10_mx25), "STC" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ask_cruk_10_mx25a), "CRUK" , Charity))

AskData$Donation <- NA
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), BHFDonation, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), OxfamDonation, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_int_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_int_hb, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_dom_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_dom_hb, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ask_stc_10_mx25, Donation ))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ask_cruk_10_mx25a, Donation ))

AskData$Happiness <- NA
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_2, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_3, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), current_happiness_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happyafter_int_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happynoask_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happynoask_1_1, Happiness))

Happiness <- AskData %>% select(Happiness, contains('happ'))
varsToKeep <- c("RiskAversion", "GeneralTrust","DecisionIntuitive", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivcorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight", "ImpairmentDescription", "code","AllDonations","happiness_1_1", "happiness_1_2", "happiness_1_3", "happiness_1", "current_happiness_1","s1happyafter_int_1", "s1happynoask_1", "s1happynoask_1_1", "Q174","Q175", "SEX", "BIRTH", "RACE", "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS",  "POWER", "ACHIEVE", "HEDON", "STIMUL", "SELFD","UNIVE", "BENEV", "TRADI", "CONFO", "SECUR", "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS", "RESPECT", "USELESS","NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL", "ANIMO", "PACT","CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1", "auth2", "auth3","auth4", "EYES1", "EYES2", "EYES3", "EYES4", "EYES5", "EYES6","EYES7", "EYES8", "EYES9", "EYES10", "EYES11", "EYES12", "EYES13","EYES14", "EYES15", "EYES16", "EYES17", "EYES18", "RISK", "trust","decisionmode", "Gender2", "BirthData","Ethnicity", "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3", "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "ImportantPower", "ImportantSuccess", "ImportantHedonsim", "ImportantStimulation","ImportantCreativity", "ImportantUniversalism", "ImpportantBenevolence", "ImportantTradition", "ImportantConformity", "ImportantSecurity", "SelfEsteemWorth", "SelfEsteemQuality", "SelfEsteemFailure", "SelfEsteemGoodWork", "SelfEsteemNoProud", "SelfEsteemPositive", "SelfEsteemSatisfied", "SelfEsteemLittleRespect", "SelfEsteemUseless", "SelfEsteemNoGood", "LinguistTestSpace", "LinguistTestBroaden","LinguistTestEmanate", "LinguistTestEdible", "LinguistTestAnimosity", "LinguistTestPact")

varsToKeep <- c("RiskAversion", "GeneralTrust", "code", "SEX", "BIRTH", "RACE", "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "RISK", "trust", "BirthData", "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK",  "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "StartDate", "EndDate")

AskData <-AskData %>% select(code, Stage, CharityTreat, Charity, Donation, Happiness, Student, one_of(varsToKeep)) %>% group_by(code)

AskData %>% ungroup() %>% group_by(Charity,Stage,CharityTreat) %>% drop_na(Donation) %>% ggplot(aes(x = as.factor(Stage), y = Donation, color = CharityTreat )) + stat_summary(fun.y=mean, geom="point", shape=18, size=3)

AskDataNA <- AskData %>% filter(!is.na(Donation) & is.na(code))


```
