---
title: "Import and tidy data"
author: "Gerhard Riener and David Reinstein"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---


# Load Packages
```{r message=FALSE, warning=FALSE}
library("tidyverse")
library("broom")
library("dataMaid")
library("qualtRics")
```

  
# Import data 

## Omnibus-linked study
Trying alternate input:
DR, @GR -- the "readSurvey" function doesn't do much I guess 

```{r message=FALSE, warning=FALSE}
col_names_S1 <- names(read_csv("../data/StudentsFirstAsk_full.csv", n_max = 0))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow? @GR I think we shall keep it. 

col_description_S1 <- names(read_csv("../data/StudentsFirstAsk_full.csv", n_max = 0,skip=1))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow?

StudentsFirstAsk_full <- read_csv("../data/StudentsFirstAsk_full.csv", col_names = col_names_S1, skip = 3)
```


Note: These are imported from .csv  files downloaded from Qualtrics.

```{r message=FALSE, warning=FALSE}

col_names <- names(read_csv("../data/NonstudentsFirstAsk.csv", n_max = 0))  #DR: this was downloaded without editing out that weird row, so we needed to recover column names @GR: note that the second row is a description of the variable names -- shall we keep this somehow?

NonstudentsFirstAsk <- read_csv("../data/NonstudentsFirstAsk.csv", col_names = col_names, skip = 3)
NonstudentsSecondAsk <- read_csv("../data/NonstudentsSecondAsk.csv")
StudentsFirstAsk <- read_csv("../data/StudentsFirstAsk.csv")
StudentsSecondAsk <- read_delim("../data/StudentsSecondAsk.csv", "\t", escape_double = FALSE, trim_ws = TRUE) #somehow this one was tab delimited 

```

*DR:* I suggest we might deal with the 'omnibus survey responses' as separate files and separate code blocks. These are coded slightly differently for students and nonstudents. Also, these come with the 'second ask' for nonstudents but with the 'first ask' for students.

### First ask

Stack students and non-students

```{r warning=FALSE}
#Start and end dates (times?) in R format for Omnibus:  
StudentsFirstAsk$StartDate<-as.POSIXct(StudentsFirstAsk$StartDate, tz = "GMT")
StudentsFirstAsk$EndDate<-as.POSIXct(StudentsFirstAsk$EndDate, tz = "GMT")
StudentsFirstAsk$RecordedDate<-as.POSIXct(StudentsFirstAsk$RecordedDate, tz = "GMT") #DR: I think this only differs if we 'closed' an unfinished survey
StudentsFirstAsk$Finished<-as.logical(StudentsFirstAsk$Finished)

StudentsFirstAsk$Student <- rep(1,nrow(StudentsFirstAsk)) #A vector of 1's to define this as a 'student'

NonstudentsFirstAsk$Finished<-as.logical(NonstudentsFirstAsk$Finished)
NonstudentsFirstAsk$Student <- rep(0,nrow(NonstudentsFirstAsk))
NonstudentsFirstAsk$code <- as.character(NonstudentsFirstAsk$RecruitmentID)
NonstudentsFirstAsk$code <- ifelse(is.na(NonstudentsFirstAsk$code), as.character(NonstudentsFirstAsk$recruitmentid), NonstudentsFirstAsk$code )


FirstAsk <- bind_rows(StudentsFirstAsk,NonstudentsFirstAsk) #stacks the rows for students and nonstudents; hope they have the same variable names

FirstAsk <- filter(FirstAsk, firstasktreat == "noask" | firstasktreat == "international_ha" | firstasktreat == "international_hb" | firstasktreat == "domestic_happyafter" | firstasktreat == "domestic_happyfirst" | firstasktreat == "domestic_ha" | firstasktreat == "domestic_hb"  | firstasktreat == "international_happybefore" | firstasktreat == "international_happyafter") #Removes before/after treatments here. (DR: might later recover for fancy statistics?)
FirstAsk$Stage <- 1
```

### Second ask
```{r}
NonstudentsSecondAsk$Finished<-as.logical(NonstudentsSecondAsk$Finished)
StudentsSecondAsk$Finished<-as.logical(StudentsSecondAsk$Finished)

StudentsSecondAsk$StartDate <- as.POSIXct(StudentsSecondAsk$StartDate,"%d.%m.%Y %H:%M", tz = "GMT")
StudentsSecondAsk$EndDate <- as.POSIXct(StudentsSecondAsk$EndDate, "%d.%m.%Y %H:%M",tz = "GMT")

NonstudentsSecondAsk$StartDate <- as.POSIXct(NonstudentsSecondAsk$StartDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$EndDate <- as.POSIXct(NonstudentsSecondAsk$EndDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$RecordedDate <- as.POSIXct(NonstudentsSecondAsk$RecordedDate, "%d/%m/%Y %H:%M",tz = "GMT")
NonstudentsSecondAsk$code <- as.character(NonstudentsSecondAsk$RecruitmentID)
NonstudentsSecondAsk$code <- ifelse(is.na(NonstudentsSecondAsk$code), as.character(NonstudentsSecondAsk$RecruitmentID), NonstudentsSecondAsk$code )


SecondAsk <- bind_rows(StudentsSecondAsk,NonstudentsSecondAsk)
SecondAsk$Stage <- 2

```

### Stack first and second ask
```{r message=FALSE, warning=FALSE, include=FALSE}

AskData <- bind_rows(FirstAsk, SecondAsk)
  
AskData <- AskData[colSums(!is.na(AskData)) > 0] #@removes rows with only missing data 

AskData$happiness_1_2 <- as.factor(AskData$happiness_1_2)
AskData$happiness_1   <- as.factor(AskData$happiness_1)
AskData$happiness_1_3 <- as.factor(AskData$happiness_1_3)
AskData$happiness_1_1 <- as.factor(AskData$happiness_1_1)

DonationVars <- c("s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb", "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb")

AskData$AllDonations <- rowSums(AskData[,DonationVars], na.rm=TRUE)

#DR: maybe keep fewer variables here, or at least put aside the omnibus survey variables and deal with these later

VarNames2 <- c("LinguistTestCloistered", "LinguistTestCaprice", "LinguistTestAccustom", "LinguistTestAllusion", "ImportantIndependence", "ImportantCuriosity", "ImportantSelfReliance", "ImportantConsiderate", "Q113", "Q114", "Q115", "Q116","Q117", "Q118", "Q120", "Q121", "Q122", "Q123", "Q124", "Q125","Q127", "Q128", "Q129", "Q130", "Q131", "Q132", "RiskAversion", "GeneralTrust","DecisionIntuitive", "Q149_1", "Q149_2", "Q149_3", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivcorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight", "ImpairmentDescription", "StartDate", "EndDate", "Stage")

keepVars <- c("ResponseId","code","RecruitmentID","AllDonations","s1_don_int_ha", "OxfamDonation", "BHFDonation",  "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb",  "ns2_don_dom_ha","S1Donation","ns1_dondom_ha",  "s1_don_int_hb", "ns2_don_int_hb",  "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb", "happiness_1_1", "happiness_1_2",  "happiness_1_3", "happiness_1", "current_happiness_1", "s1happyafter_int_1",  "s1happynoask_1", "s1happynoask_1_1", "Q174", "Q175", "SEX", "BIRTH", "RACE", "RELIG",  "SINGLE", "UNI STDNT", "STUDIES", "PREV PAR", "EXP PREF", "MOMJOB",  "DADJOB", "MOMEDUC", "DADEDUC", "SIBLINGS", "SIBORDER", "CHILD",  "NUMCHILD", "birth_nation", "ABROAD", "NATION", "ENGYEARS", "FIRSTLANG",  "FLUENT", "HOMELANG", "LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2",  "OTR_COUNTRY1_3", "OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3",  "ATTRIBUTES_1", "ATTRIBUTES_2", "ATTRIBUTES_3", "ATTRIBUTES_4",  "ATTRIBUTES_5", "ATTRIBUTES_6", "ATTRIBUTES_7", "ATTRIBUTES_8",  "ATTRIBUTES_9", "ATTRIBUTES_10", "POWER", "ACHIEVE", "HEDON",  "STIMUL", "SELFD", "UNIVE", "BENEV", "TRADI", "CONFO", "SECUR",  "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS",  "RESPECT", "USELESS", "NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL",  "ANIMO", "PACT", "CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1",  "auth2", "auth3", "auth4", "EYES1", "EYES2", "EYES3", "EYES4",  "EYES5", "EYES6", "EYES7", "EYES8", "EYES9", "EYES10", "EYES11",  "EYES12", "EYES13", "EYES14", "EYES15", "EYES16", "EYES17", "EYES18",  "RISK", "trust", "decisionmode", "likert_time_recip_1", "likert_time_recip_2",  "likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1",  "social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5",  "ineq", "ownership", "merit", "IMPAIR", "MENT",   "gender",  "firstasktreat", "S1Reward", "Student",   "sex", "childpresentmdl",  "clustergroup", "ordergroup", "recruitmentid", "title", "rand_num",  "rankingroup", "groupn", "reminderperson",  "Gift", "BHFExtra", "OxfamExtra", "TotalExtra",   "salaryrequest1", "medsalaryguess",  "salaryrequest2",  "Q23",  "guesspctwork",  "guessavgsalary",   "Q17_1_TEXT", "Q17_2_TEXT", "Q17_3_TEXT", "Q17_4_TEXT",  "Q18_1_TEXT", "Q18_2_TEXT", "Q18_3_TEXT", "Q18_4_TEXT",  "ask_stc_10_mx25", "ask_cruk_10_mx25a",  "Q144", "Q145", "Q46", "Q47", "Q48", "Q49", "Q50", "Q53", "Q54", "Q56", "Q57", "Q58", "Q59", "Q60", "Q61", "Q62",  "Q63", "Q64", "Q65", "Q66", "Q67", "Q68", "Q69", "Q70", "Q71",  "Q72_1", "Q72_2", "Q72_3", "Q73_1", "Q73_2", "Q73_3", "Q75_1",  "Q75_2", "Q75_3", "Q75_4", "Q75_5", "Q75_6", "Q75_7", "Q75_8",  "Q75_9", "Q75_10", "Q77", "Q78", "Q79", "Q80", "Q81", "Q83",  "Q84", "Q85", "Q86", "Q87", "Q89", "Q90", "Q91", "Q92", "Q93",  "Q95", "Q96", "Q97", "Q98", "Q99", "Q101", "Q102", "Q103", "Q104",  "Q105", "Q107", "Q108", "Q109", "Q110", "Q111", "Q151", "Q152",  "Q153", "Q154", "Q113", "Q114", "Q115", "Q116", "Q117", "Q118",  "Q120", "Q121", "Q122", "Q123", "Q124", "Q125", "Q127", "Q128",  "Q129", "Q130", "Q131", "Q132", "Q146", "Q147", "Q148", "Q149_1",  "Q149_2", "Q149_3", "Q134", "Q135", "Q136_1", "Q136_2", "Q136_3",  "Q136_4", "Q136_5", "Q138", "Q139", "Q140", "Q141", "Q142",  "StartDate", "EndDate", "Stage","DistributionChannel", "Duration (in seconds)") #@keepVars

# Variables names for renaming

VarNames1 <- c("ResponseId", "code", "RecruitmentID","AllDonations","s1_don_int_ha", "OxfamDonation", "BHFDonation", "TotalDonation", "ns1_donint_ha", "ns2_don_dom_hb", "ns2_don_dom_ha", "S1Donation", "ns1_dondom_ha", "s1_don_int_hb", "ns2_don_int_hb", "ns2_don_int_ha", "s1_don_dom_ha", "s1_don_dom_hb", "happiness_1_1", "happiness_1_2", "happiness_1_3", "happiness_1", "current_happiness_1","s1happyafter_int_1", "s1happynoask_1", "s1happynoask_1_1", "Q174","Q175", "sex", "birth", "race", "relig", "single", "uni stdnt","studies", "prev par", "exp pref", "momjob", "dadjob", "momeduc","dadeduc", "siblings", "siborder", "child", "numchild", "birth_nation","abroad", "nation", "engyears", "firstlang", "fluent", "homelang","langs", "otr_country1_1", "otr_country1_2", "otr_country1_3","otr_country2_1", "otr_country2_2", "otr_country2_3", "attributes_1","attributes_2", "attributes_3", "attributes_4", "attributes_5","attributes_6", "attributes_7", "attributes_8", "attributes_9","attributes_10", "power", "achieve", "hedon", "stimul", "selfd","unive", "benev", "tradi", "confo", "secur", "worth", "goodq", "fail", "compar", "proud", "posat", "satis", "respect", "useless","nogood", "space", "broad", "emana", "edibl", "animo", "pact","clois", "capri", "accus", "allus", "auth1", "auth2", "auth3","auth4", "eyes1", "eyes2", "eyes3", "eyes4", "eyes5", "eyes6","eyes7", "eyes8", "eyes9", "eyes10", "eyes11", "eyes12", "eyes13","eyes14", "eyes15", "eyes16", "eyes17", "eyes18", "risk", "trust","decisionmode", "likert_time_recip_1", "likert_time_recip_2","likert_time_recip_3", "pol_interest", "POLIT", "social_ideo_1","social_ideo_2", "social_ideo_3", "social_ideo_4", "social_ideo_5","ineq", "ownership", "merit", "ImpairmentHearSight", "ImpairmentDescription", "gender","firstasktreat", "S1Reward", "Student", "Sex", "childpresentmdl","clustergroup", "ordergroup", "recruitmentid", "title", "rand_num","rankingroup", "groupn", "reminderperson", "Gift", "BHFExtra","OxfamExtra", "TotalExtra", "salaryrequest1",   "medsalaryguess",  "salaryrequest2", "Q23",    "guesspctwork", "guessavgsalary",  "Q17_1","Q17_2", "Q17_3", "Q17_4", "Q18_1", "Q18_2","Q18_3", "Q18_4", "ask_stc_10_mx25", "ask_cruk_10_mx25a", "Q144", "Q145", "Gender2", "BirthData","Ethnicity", "Religion", "MaritalStatus", "PreviousExperiment", "PreferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3", "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "ImportantPower", "ImportantSuccess", "ImportantHedonism", "ImportantStimulation","ImportantCreativity", "ImportantUniversalism", "ImportantBenevolence", "ImportantTradition", "ImportantConformity", "ImportantSecurity", "SelfEsteemWorth", "SelfEsteemQuality", "SelfEsteemFailure", "SelfEsteemGoodWork", "SelfEsteemNoProud", "SelfEsteemPositive", "SelfEsteemSatisfied", "SelfEsteemLittleRespect", "SelfEsteemUseless", "SelfEsteemNoGood", "LinguistTestSpace", "LinguistTestBroaden","LinguistTestEmanate", "LinguistTestEdible", "LinguistTestAnimosity", "LinguistTestPact")

VarNames2 <- c("LinguistTestCloistered", "LinguistTestCaprice", "LinguistTestAccustom", "LinguistTestAllusion", "ImportantIndependence", "ImportantCuriosity", "ImportantSelfReliance", "ImportantConsiderate", "Eyes1", "Eyes2",	"Eyes3",	"Eyes4",	"Eyes5","Eyes6","Eyes7",	"Eyes8",	"Eyes9",	"Eyes10",	"Eyes11",	"Eyes12", "Eyes13", "Eyes14", "Eyes15", "Eyes16", "Eyes17",	"Eyes18", "RiskAversion", "GeneralTrust","DecisionIntuitive", "Patience", "CostlyPunisherDirect", "CostlyPunisherIndirect", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight0", "ImpairmentDescription0", "StartDate", "EndDate", "Stage","DistributionChannel", "Duration")

# Further fixes

AskData$firstasktreat <- ifelse(is.na(AskData$firstasktreat) & is.na(AskData$OxfamDonation), "international_happyfirst", AskData$firstasktreat)
    

VarNames <- c(VarNames1,VarNames2)


AskData <- select(AskData, keepVars)

VarNames <- c(VarNames1,VarNames2)
colnames(AskData) <- VarNames



```

### Merge data columns

We have a lot of variables that record the same but are labeled differently in different experiments. Try to merge those. DR: Maybe Anca can help with this


```{r}
#DR: I assume this is making common variable names/labels for key variables across the surveys @DR: Yes at least it is a first try, there seem to be many more

varsReplace <- c("SEX", "BIRTH", "RACE")#, "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS", "OTR_COUNTRY1_1", "OTR_COUNTRY1_2", "OTR_COUNTRY1_3","OTR_COUNTRY2_1", "OTR_COUNTRY2_2", "OTR_COUNTRY2_3")

varsKeepReplace <- c("Gender2", "BirthData","Ethnicity")#, "Religion", "MaritalStatus", "PreviousExperiment", "PreferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3")

IterateReplace <- function(rd,kd) {
  AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd))
}

IterateReplace("Gender2","SEX")
IterateReplace("Sex","sex")

# AskData$BirthData <- with(AskData,ifelse(is.na(BirthData),BIRTH,BirthData))

mapply(function(rd,kd) AskData$rd <- with(AskData,ifelse(is.na(rd),kd,rd), rd = varsKeep, rd = varsKeepReplace))

# Save merged data @DR took this out as I do not think this is necessary at this stage. We can do this once we have the full dataset
# write_csv(AskData, "../output/AskData.csv") 

```
**Comments on above chunk**
- DR, @GR: Not sure the "mapply" statement is working
  - Also, is there a quicker way to do this in general for all cases where the variable names are the same except for capitalization?
- DR, @GR: Wouldn't it be better for us to do the variable renaming for the nonstudents and students separately, so these have the same names, and then when we stack these the variables will be the same?


### Tidy data
**DR: The following should define the treatments**

- Nonstudents: firstasktreat (same variable in both csv files) for first ask, combined with whichever is nonmissing among (ns2_don_int_hb, ns2_don_int_ha, ns2_don_dom_hb, ns2_don_dom_ha) for the second ask (if one of the first two are present it is the international second ask, if one of the latter two are present it's the domestic second ask).
  - In the raw data I find 97 entries with a firstasktreat recorded as well as a nonmissing value for one of the aforementioned ns2 variables.

- Students:  firstasktreat (same variable in both csv files) for first ask, combined with whichever is nonmissing among ask_stc_10_mx25 and ask_cruk_10_mx25a for the second ask (the former is international, the latter is domestic).  
  - In the raw data I find 142 obs with a firstasktreat recorded as well as a nonmissing value for one of ask_stc... or ask_cruk... 

```{r}
#coding the main treatment "CharityTreat"

#First for students


AskData <- AskData %>% mutate(CharityTreatf = case_when(!is.na(ask_cruk_10_mx25a) & str_detect(firstasktreat,"domestic")  ~ "Domestic-Domestic",
                                                       !is.na(ask_stc_10_mx25) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Internat.",
                                                       !is.na(ask_cruk_10_mx25a) & str_detect(firstasktreat,"international")   ~ "Internat.-Domestic",
                                                       !is.na(ask_stc_10_mx25) & str_detect(firstasktreat,"international") ~ "Internat.-Internat.",
                                                       !is.na(ask_cruk_10_mx25a) & firstasktreat == "noask"  ~ "No ask-Domestic",
                                                       !is.na(ask_stc_10_mx25) & firstasktreat == "noask"  ~ "No ask-Internat.",
                                                       !is.na(ns2_don_dom_hb) & firstasktreat == "noask"  ~ "No ask-Domestic",
                                                       !is.na(ns2_don_dom_ha) & firstasktreat == "noask"  ~ "No ask-Domestic",
                                                       !is.na(ns2_don_int_hb) & firstasktreat == "noask"  ~ "No ask-Internat.",
                                                       !is.na(ns2_don_int_ha) & firstasktreat == "noask"  ~ "No ask-Internat.",
                                                       !is.na(ns2_don_dom_hb) & str_detect(firstasktreat,"domestic")  ~ "Domestic-Domestic",
                                                       !is.na(ns2_don_dom_ha) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Domestic",
                                                       !is.na(ask_cruk_10_mx25a) & str_detect(firstasktreat,"international")   ~ "Internat.-Domestic",
                                                       !is.na(ask_stc_10_mx25) & str_detect(firstasktreat,"international") ~ "Internat.-Internat.",
                                                       !is.na(ns2_don_dom_hb) & str_detect(firstasktreat,"domestic")  ~ "Domestic-Domestic",
                                                       !is.na(ns2_don_dom_ha) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Domestic",
                                                       !is.na(ns2_don_int_hb) & str_detect(firstasktreat,"domestic")  ~ "Domestic-Internat.",
                                                       !is.na(ns2_don_int_ha) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Internat.",
                                                       !is.na(ns2_don_int_hb) & str_detect(firstasktreat,"international")  ~ "Internat.-Internat.",
                                                       !is.na(ns2_don_int_ha) & str_detect(firstasktreat,"international")   ~ "Internat.-Internat.",
                                                       !is.na(ns2_don_dom_hb) & str_detect(firstasktreat,"international")  ~ "Internat.-Domestic",
                                                       !is.na(ns2_don_dom_ha) & str_detect(firstasktreat,"international")   ~ "Internat.-Domestic"
                                                      )) 

#Next for for nonstudents
#(ns2_don_int_hb, ns2_don_int_ha, ns2_don_dom_hb, ns2_don_dom_ha) 
 #WIP AskData <- AskData %>% mutate(CharityTreatf = case_when(!is.na(ns2_don_dom_hb) & str_detect(firstasktreat,"domestic")  ~ "Domestic-Domestic", !is.na(ns2_don_dom_ha) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Domestic", !is.na(ns2_don_int_hb) & str_detect(firstasktreat,"domestic")   ~ "Domestic-Internat.", !is.na(ns2_don_int_hb) & str_detect(firstasktreat,"international")   ~ "Internat.-Domestic", !is.na(ask_stc_10_mx25) & str_detect(firstasktreat,"international") ~ "Internat.-Internat.", !is.na(ask_cruk_10_mx25a) & firstasktreat == "noask"  ~ "No ask-Domestic", !is.na(ask_stc_10_mx25) & firstasktreat == "noask"  ~ "No ask-Internat." ))  

AskData$CharityTreatf <- as.factor(AskData$CharityTreatf)

AskData$Charity <- NA
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(BHFDonation), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(OxfamDonation), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_int_ha), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_int_hb), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_dom_ha), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(s1_don_dom_hb), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns2_don_int_ha), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns2_don_int_hb), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns2_don_dom_ha), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns2_don_dom_hb), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns1_donint_ha), "Oxfam" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ns1_dondom_ha), "BHF" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ask_stc_10_mx25), "STC" , Charity))
AskData <- AskData %>% mutate(Charity = ifelse(!is.na(ask_cruk_10_mx25a), "CRUK" , Charity))

AskData$Donation <- NA
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), BHFDonation, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), OxfamDonation, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_int_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_int_hb, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_dom_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), s1_don_dom_hb, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ask_stc_10_mx25, Donation ))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ask_cruk_10_mx25a, Donation ))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns1_donint_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns1_dondom_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns2_don_int_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns2_don_int_hb, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns2_don_dom_ha, Donation))
AskData <- AskData %>% mutate(Donation = ifelse(is.na(Donation), ns2_don_dom_hb, Donation))

AskData$Happiness <- NA
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_2, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1_3, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), happiness_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), current_happiness_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happyafter_int_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happynoask_1, Happiness))
AskData <- AskData %>% mutate(Happiness = ifelse(is.na(Happiness), s1happynoask_1_1, Happiness))

Happiness <- AskData %>% select(Happiness, contains('happ'))
varsToKeep <- c("RiskAversion", "GeneralTrust","DecisionIntuitive", "InterestedPolitics", "PoliticAttitudeLeftRight", "JustifiedHomosexuality","JustifiedProstitution", "JustifiedAbortion", "JustifiedDivcorce", "JustifiedSex", "AgreeInequality", "AgreegovernmentOwnership", "AgreeHardWork","ImpairmentHearSight", "ImpairmentDescription", "code","AllDonations","happiness_1_1", "happiness_1_2", "happiness_1_3", "happiness_1", "current_happiness_1","s1happyafter_int_1", "s1happynoask_1", "s1happynoask_1_1", "Q174","Q175", "SEX", "BIRTH", "RACE", "RELIG", "SINGLE", "UNI STDNT","STUDIES", "PREV PAR", "EXP PREF", "MOMJOB", "DADJOB", "MOMEDUC","DADEDUC", "SIBLINGS", "SIBORDER", "CHILD", "NUMCHILD", "birth_nation","ABROAD", "NATION", "ENGYEARS", "FIRSTLANG", "FLUENT", "HOMELANG","LANGS",  "POWER", "ACHIEVE", "HEDON", "STIMUL", "SELFD","UNIVE", "BENEV", "TRADI", "CONFO", "SECUR", "WORTH", "GOODQ", "FAIL", "COMPAR", "PROUD", "POSAT", "SATIS", "RESPECT", "USELESS","NOGOOD", "SPACE", "BROAD", "EMANA", "EDIBL", "ANIMO", "PACT","CLOIS", "CAPRI", "ACCUS", "ALLUS", "auth1", "auth2", "auth3","auth4", "EYES1", "EYES2", "EYES3", "EYES4", "EYES5", "EYES6","EYES7", "EYES8", "EYES9", "EYES10", "EYES11", "EYES12", "EYES13","EYES14", "EYES15", "EYES16", "EYES17", "EYES18", "RISK", "trust","decisionmode", "Gender2", "BirthData","Ethnicity", "Religion", "MaritalStatus", "PreviousExperiment", "PReferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK", "LivedOtherCountries1", "LivedOtherCountries2", "LivedOtherCountries3", "YearsOtherCountries1","YearsOtherCountries2","YearsOtherCountries3", "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "ImportantPower", "ImportantSuccess", "ImportantHedonsim", "ImportantStimulation","ImportantCreativity", "ImportantUniversalism", "ImpportantBenevolence", "ImportantTradition", "ImportantConformity", "ImportantSecurity", "SelfEsteemWorth", "SelfEsteemQuality", "SelfEsteemFailure", "SelfEsteemGoodWork", "SelfEsteemNoProud", "SelfEsteemPositive", "SelfEsteemSatisfied", "SelfEsteemLittleRespect", "SelfEsteemUseless", "SelfEsteemNoGood", "LinguistTestSpace", "LinguistTestBroaden","LinguistTestEmanate", "LinguistTestEdible", "LinguistTestAnimosity", "LinguistTestPact")

  varsToKeep <- c("RiskAversion", "GeneralTrust", "code", "sex", "birth", "race", "relig", "single", "uni stdnt","studies", "prev par", "exp pref", "momjob", "dadjob", "abroad","momeduc","dadeduc", "siblings", "siborder", "child", "numchild", "risk", "trust", "BirthData", "Religion", "MaritalStatus", "PreviousExperiment", "PreferenceExperiment", "OccupationMother", "OccupationFather", "EducationMother", "EducationFather","Siblings", "SiblingsOlder", "Children", "ChildrenNumber", "BornUK", "BornCountry", "YearsInUK", "LanguageEnglishFirst", "LanguageEnglishFluent","LanguageMainChildhood","LanguageOther",  "LivedOutsideUK",  "PersonalityExtroverted", "PersonalityCritical", "PersonalityDependable", "PersonalityAnxious", "PersonalityOpen", "PersonalityReserved","PersonalitySympathetic", "PersonalityCareless", "PersonalityCalm", "Personalityconventional", "StartDate", "EndDate")

AskData <-AskData %>% select(code, Stage, CharityTreatf, Charity, Donation, Happiness, Student, one_of(varsToKeep)) %>% group_by(code) 
# %>% #filter((!is.na(Donation)& Stage == 2) |Stage == 1)

AskData <- AskData %>% arrange(code, desc(Stage)) %>% fill(CharityTreatf) 

AskDataNA <- AskData %>% filter(!is.na(Donation) & is.na(code))


```

*Comments on previous chunk:*

- DR, @GR: Why are we dropping/keeping these specific variables?
  - Note I changed the capitalisation on some variables and we need to adjust to that
  
- DR, 14 May 2018: I shortened the variable coding for students (tested as identical) and add(ing) the nonstudent bit now

- DR 21 May 2018: There are 2 lists of "VarsToKeep" -- why? which was intended?

## Exeter Piggy back

```{r Import piggy back, message=FALSE, warning=FALSE, paged.print=FALSE}
AskDataExeter <- read_csv("../data/substitution_giving_data_exeter1-round1_round2.csv")
AskDataExeter$`date-time-s1` <- as.POSIXct(AskDataExeter$`date-time-s1`, tz = "GMT", "%y%m%d_%H%M")

AskDataExeter <- AskDataExeter %>% 
  rename( donationpresent_1 = donation_present, donationstated_1 = donation_stated, happiness_1 = happiness, satisfiedexperiment_1 = satisfied_experiment, countingorder_1 = countingorder, happiness_2 = happiness2, donationpresent_2 = donation_present2, donationstated_2 = donation_stated2, countingorder_2 = countingorder2, ID = `Participant number`) %>%
  mutate(earnings_1 = Earnings_check + gamble_check) %>% 
  select(everything(),-dropflag, -satisfiedexperiment_1, -comments, -comments_1, -Earnings_check, -gamble_check, -countingorder_1, -countingorder_2)

AskDataExeter <- AskDataExeter %>% 
gather(key = variable, value, donationpresent_1, donationpresent_2, donationstated_1, donationstated_2, happiness_1, happiness_2, earnings_1, earnings_2, -ID, -Treatment , na.rm = FALSE, convert = TRUE) %>% 
  separate(variable, into = c("Variable", "Stage"), sep = "_") %>% 
  spread(key = Variable, value = value) %>% replace_na(list(donationpresent = 0)) %>% mutate(Donation = as.numeric(donationpresent), Treatment = as.factor(Treatment), Stage = as.factor(Stage)) 

#note: this "gather" followed by "seperate" and "spread" turns data from wide to long... when we 'pipe' into the gather function we don't need to specify the first argument, the data frame

AskDataExeter$Treatment <-  fct_recode(AskDataExeter$Treatment, "No ask - UNICEF" = "0" , "Oxfam - UNICEF" = "1", "WWF - UNICEF" = "2")


```

*Comments on previous chunk:*
- DR @GR: I don't think we want to sum Earnings_check and gamble_check; why did you think so? 


#Some Stata code that might be useful to integrate in:

##Categorizing variables
  global OUTCOMES Donation Donated DonatedAll DonatedNothing Happiness choosechar
  global TREATMENTS Treatment WonPrize
  global CHARACTERISTICS Gender Age RelConfession Race UniStudent FirstLangEng FluentEng YearsEnglish NativeLanguage BirthNationUK Nation Siblings SiblBirthOrder MaritalStatus Child ChildrenNo LivedAbroad ImpairC EducationMother EducationFather WorkMother WorkFather BirthDate
  global PERSONALITY RiskAttitude TrustGeneral PersExtrovert PersCritical PersDependable PersAnxious PersOpenness PersReserved PersSympathetic PersCareless PersCalm PersConventional ValueAchieve ValueStimu ValueSelfDir ValueBenevol ValueTradition ValueConformity ValueSecurity PersWorth PersQuality ValuePower ValueHedon ValueUniversal PersFail PersCompar PersNotProud PersPosAtt PersSatisfied PersNoRespect PersUseless PersNoGood
  global ATTITUDES AuthoritarianValues1 AuthoritarianValues2 AuthoritarianValues3 AuthoritarianValues4 IdeologyHomosexuality IdeologyProstitution IdeologyAbortion IdeologyDivorce IdeologySex
  global METADATA code StartDate EndDate Progress Durationinseconds Finished RecordedDate ResponseId FinishedSurvey ExperimentParticipation

